Work Fragmentation in Developer Interaction Data

### 2016-02-10 paper_2.tex
RQ4

We did so by computing Cohen's $d$ on the quantity of edits before and after the interruption. To obtain a significant effect, we need the presence of activity both before and after the interruption. Not all the interruptions meet this criteria however: some are located close to the start or the end of a session, or too close to another interruption (in this, the next interruption would ``disturb'' the observation).  In total, 53\% of the interruptions had 30 minutes before and after the interruption and were selected for the analysis.  The remaining 47\% of the interruptions can not be used on this analysis due to the lack of time around them. %We used the Algorithm \ref{alg:local_effect} for the classification, and the 
Table \ref{tbl:local_effect} shows the applied thresholds and the results, accompanied with a typical example of an interruption in each category. This local analysis shows that there are indeed three well-defined groups of interruptions, with the two largest of them having clear effects on the activity in the session.

@@

We established the recovery time as the 15 minutes period after an interruption, without considering the time consumed by the interruption itself. The length of the period was chosen according to the observations by Solingen et al. \cite{SBV98}, who explain that although it is a variable difficult to measure, estimating 15 minutes for this phase is believed to be valid. They also consider the recovery time as the third (and last) phase of an interruption; the first one is the occurrence phase, or the start interruption, followed by the handling phase that contains all the activities required by the interruption.

@@

In order to execute this analysis, it was necessary to make a selection of the interruptions that have a period after it of at least 15 minutes of recorded work, before another interruption occurs. After this query we obtained 5,684 valid interruptions from a total of 110,077.

@@

\begin{itemize}
	\item \textit{Before interruption}: a period of 10 minutes before the next interruption.
	\item \textit{Peak}: the time between the recovery time and the before interruption phase.
\end{itemize}

@@

\begin{figure}[!ht]
	\centering
	\begin{tabular}{c}
		\includegraphics[width=.9\linewidth,clip=, angle=0]{figures/udc_after_Interruption} \\
	\end{tabular}
	\caption{Graphic showing how the time after an interruption was split. }
	\label{fig:recovery_afterRecovery}
\end{figure}

@@

We can see in the Figure \ref{fig:box_recovery_udc} the evolution of the metrics through
the phases. The three metrics show a tendency to increase and reach a maximum between the last phase of the recovery time and the peak of the session. Moreover, the fall of the productivity on the last minutes before the next interruptions agrees with the observations on the local analysis of the time around an interruption. From this we can conclude that the first five minutes after an interruption and the moment before the next one are the are the phases where productivity is more affected, while the phases around the peak are where the productivity is more favorable.

>>>>

We did so by computing Cohen's $d$ on the quantity of edits before and after the interruption. To obtain a significant effect, we need the presence of activity both before and after the interruption. Not all the interruptions meet this criteria however: some are located close to the start or the end of a session, or too close to another interruption.  In total, 53\% of the interruptions had 30 minutes before and after the interruption and were selected for the analysis.  The remaining 47\% of the interruptions can not be used on this analysis due to the lack of time around them. %We used the Algorithm \ref{alg:local_effect} for the classification, and the 
Table \ref{tbl:local_effect} shows the applied thresholds and the results, accompanied with a typical example of an interruption in each category. This local analysis shows that there are indeed three well-defined groups of interruptions, with the two largest of them having clear effects on the activity in the session.

@@

We established the recovery time as the 15 minutes period after an interruption, without considering the time consumed by the interruption itself. The length of the period was chosen according to the observations by Solingen et al. \cite{SBV98}, who explain that although it is a variable difficult to measure, estimating 15 minutes for this phase is believed to be valid. They also consider the recovery time as the third (and last) phase of an interruption; the first one is the occurrence phase, or the start of the interruption, followed by the handling phase that contains all the activities required by the interruption.

@@

In order to execute this analysis, it was necessary to select only the interruptions that have a period after them of at least 15 minutes of recorded work, before another interruption occurs (as the subsequent interruption would ``pollute'' the data for the purposes of this analysis). After this filtering we obtained 5,684 valid interruptions from a total of 110,077.

@@

\begin{itemize}
	\item \textit{Before interruption}: a period of 10 minutes before the next interruption.
	\item \textit{Peak}: the time between the recovery time and the ``before interruption'' phase.
\end{itemize}

@@

\begin{figure}[!ht]
	\centering
	\begin{tabular}{c}
		\includegraphics[width=.9\linewidth,clip=, angle=0]{figures/udc_after_Interruption} \\
	\end{tabular}
	\caption{How we split the time after an interruption. }
	\label{fig:recovery_afterRecovery}
\end{figure}

@@

We can see in the Figure \ref{fig:box_recovery_udc} the evolution of the metrics through
the phases. The three metrics show a tendency to increase and reach a maximum between the last phase of the recovery time and the peak of the session. Moreover, the fall of the productivity on the last minutes before the next interruptions agrees with the observations on the local analysis of the time around an interruption. From this we can conclude that the first five minutes after an interruption and the moment before the next one are the are the phases where productivity is more affected, while the phases around the peak are where the productivity is the highest.
